\documentclass{article}


\title{Javascript API}
\author{Charles Deluce}

\begin{document}

\section{Functions}
Functions

\subsection{Data Viewer}

\subsubsection{change_class()}
Called by the 'class_select' select box to choose which 
class in the loaded ction is used in displaying data.

\subsubsection{loadCtion()}
This method is called by the "ction_load" button for getting 
the ction supplied in the "ction" input.

\subsubsection{getCtion()}
The method which handles the response data from the api call.

\subsubsection{dataQuery()}
Method that responds api call for Text Data for the ction.

\subsubsection{getQuery()}
This Method handles the data from dataQuery api call.

\subsubsection{col2sort()}
Performs comparison on second column.

\subsection{Data Tree}

\subsubsection{newC()}
Method to generate new ction data.

\subsubsection{loadC()}
This method generates a panel for inputing and submitting the data
for loading an existing Ction from the api.

\subsubsection{load_ction()}
This method performs the rest call to get the data for the
specified ction.

\subsubsection{addLabel()}
Method responds to 'label_class' input to add label classes
into the 'c_select' pull-down box.

\subsubsection{save_ction()}
Method to save ction data.

\subsubsection{reqGet()}
Method that handles response to the load_ction api call.

\subsubsection{reqListener()}
Function to handle save_ction api call.

\subsubsection{change_class()}
Save as DataViewer function.

\subsubsection{handleSample()}
Handles events in Data Tree to generate sample
for vec.

\subsubsection{product_click()}
Method to display subproduct data in data tree for selected
product.

\subsubsection{subproduct_click()}
Same but for issue.

\subsubsection{issue_click()}
Same but for subissue.

\subsection{TermDefiner}

\subsubsection{radio_select()}


\subsubsection{addterm()}

\subsubsection{save_list()}

\subsubsection{new_list()}

\subsubsection{load_list()}

\subsubsection{load_name()}

\end{document}

